Windowed Developer Topic Analysis

### 2009-04-05 lda-paper.tex
my latest changes to the paper
Some changes to the paper about figures and a change to the commit to topics figure (more labels)

We propose to extend the use of common topic analysis techniques by executing
them over windows of documents over time. We hope by looking at topic
clusters over time we can identify continuous effort on a select
group of topics.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{lda}
  \caption{Example of topics extracted from MySQL 3.23. This is the kind of plot we eventually want to produce: named topics and topic trends}
  \label{fig:lda}
\end{figure*}

\section{Methodology}
\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{commit-to-topics} 
  \caption{How commits are analyzed and aggregated into Topics and Trends}
  \label{fig:commits}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{transitiveclosure}
  \caption{Clusting topics by the transitive closure of topic similarity. Nodes are topics and arcs imply similarity}
\label{fig:closure}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{fixed-time-smear-plot-scaled}
  \caption{Compact Trend Plot Topics per Month for MaxDB 7.500}
  \label{fig:topicsmear}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fixed-time-smear-plot-cropped}
  \caption{Zoomed in Slice Compact Trend Plot of Topics per Month for MaxDB 7.500}
  \label{fig:zoomedsmear}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{class-smear-plot-crop-scaled}
  \caption{Trend Time Line: Trends plotted over time of MaxDB 7.500}         
  \label{fig:trendtimeline}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{histogram-cropped-scaled}
  \caption{Top part of trend histogram, ordered by topic occurance for MaxDB 7.500}       
  \label{fig:histogram}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{maxdb7500-everything-by-month}
  \caption{MaxDB 7.500 Topics Analyzed with Static Topic Analysis, 20
    topics over the entire development history of MaxDB 7.500. Each
    box indicates the number of documents matching that topic in that
    month.}
  \label{fig:statictopics}
\end{figure}

\subsection{Validation}

>>>>

We propose to extend the use of common topic analysis techniques by
executing them over windows of documents over time. We hope by looking
at topic clusters over time we can identify continuous effort on a
select group of topics. Figure \ref{fig:lda} is an example of the kind
of visualization we want to automatically generate. We want to see
topics which are unique to a certain time period, displayed across the
time axis. Those topics that reoccur, or occur over a larger period
are plotted continuously. In our example we have summarized the topics
with a single word.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{lda}
  \caption{Example of topics extracted from MySQL 3.23. This is the kind of plot we eventually want to produce: named topics and topic trends. The horizontal axis is time in months and the vertical axis used to stack topics that occur at the same time. Longer topics are topics which reoccur in adjacent window.}
  \label{fig:lda}
\end{figure*}

\section{Methodology}
\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{commit-to-topics} 
  \caption{How commits are analyzed and aggregated into Topics and Trends. Commits are first extracted, then abstracted into word counts or word distributions. These word distributions are then given to topic clusterer like LDA which finds independant word distributions (topics) that these documents are related too and clusters or associates these documents with these topics.}
  \label{fig:commits}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{transitiveclosure}
  \caption{Clusting topics by the transitive closure (connectedness or
    a fill flood along arcs) of topic similarity. Nodes are topics and
    arcs imply similarity. Similarity could be a measure such as
    topics share 8 out of 10 top ten words.}
\label{fig:closure}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{fixed-time-smear-plot-scaled}
  \caption{Compact Trend Plot Topics per Month for MaxDB 7.500. The
    X-axis is time in months, the Y axis is used to stack topics
    occurring at the same time. Trends which are continuous are
    plotted as continuous blocks. The top 10 words in the topics are
    joined and embedded in box representing the topics.}
  \label{fig:topicsmear}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fixed-time-smear-plot-cropped}
  \caption{Zoomed in Slice Compact Trend Plot of Topics per Month for MaxDB 7.500. The topic text is visible in each topic box. Trends are plotted across time continuously.}
  \label{fig:zoomedsmear}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{class-smear-plot-crop-scaled}
  \caption{Trend Time Line: Trends plotted over time of MaxDB 7.500. Time in months are plotted along the X-Axis, each row on the Y-axis is associated with a trend ranked by size in descending order}         
  \label{fig:trendtimeline}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{histogram-cropped-scaled}
  \caption{Top part of trend histogram, ordered by topic occurance for MaxDB 7.500. X axis determines the number of continuous months of a trend. Trends are ranked  by the number of topics that a trend contains in descending order.}       
  \label{fig:histogram}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{maxdb7500-everything-by-month}
  \caption{MaxDB 7.500 Topics Analyzed with Static Topic Analysis, 20
    topics over the entire development history of MaxDB 7.500. The
    color of the topic indicates the number of documents matching that
    topic in that month relative to the number of documents (white is
    most, black is least).}
  \label{fig:statictopics}
\end{figure}

%\subsection{Validation}
